Demographic Groups with Stronger Biden Support in the Election Race

### 2024-04-02 paper/paper.qmd
update change

## Weightening
The sample use two-stage weighting process to correct the imbalances between matched sample and target population.They use a weight method called entropy balancing, which focus on attributes including gender, race, education, age, and voting behavior

## Vote Vaildation

@@

ces2022 |> slice_head(n = 10) |>
  kable(booktabs = TRUE, caption = "Brief summary of variables types") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by gender, and race
#| echo: false
#| warning: false
#| message: false

>>>>

## Weightening
To correct the imbalance between the matched samples and the overarching target demographic, a two-phase weighting procedure is employed, ensuring the CES samples accurately mirror the population's diversity. The initial phase of this adjustment process involves entropy balancing, alongside iterative proportional fitting (often termed 'raking'), to align the sample with the population's demographic and political characteristics. This includes a comprehensive evaluation of variables and their interrelations. The approach guarantees that the common content of the survey represents each state accurately, incorporating adjustments for statewide electoral contests.

## Vote Validation
Vote validation have been considered in the CES in order to verify the accuracy of the voting behaviors. The sample were matched to the TargetSmart database that include the registered voter responds. Only the records which have a high level of confidence could be matched. This process is helpful for identifying voters and the way they vote, such as absentee, early, and mail.Therefore CES can ensure the data is focused on voting behavior and accurately represent genuine voter engagement.

@@

ces2022 |> slice_head(n = 10) |>
  kable(booktabs = TRUE, caption = "Brief summary of variables types") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```
After installing `dataverse`[@dataverse], I use `get_dataframe_by_name` to analyze CES. I select four variables that most relevant to our topic, which are `votereg`, `presvote20post`, `educ`, `faminc_new`, `gunown`.  `votereg` represents the voter registration status and only the voter who registered to vote would be considered. Besides, `presvote20post` represents the president that respondents vote in 2020 president election. I only consider the respond of Joe Biden and Donald Trump. `educ` means the education level of the respondents. In addition, `faminc_new` accounts for the family's annual income in 2021 year. `gunown` records the personal gun ownership by asking the respondent to answer whether they or anyone in their household own a gun.
```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by gender, and race
#| echo: false
#| warning: false
#| message: false
